---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# The `devel` set of functions


## Overview

This "package" is the development package. Do not attempt to load it as you
would a typical package. It contains a loose testing ground of functionality
that, if deemed sufficiently useful, will eventually be migrated into an
appropriate member of the `somaverse`.


----------------------------

## Installation

You cannot currently install the `devel` library from the command line, as 
it is not a package *per se*. The simplest way to optain the functionality
it contains is to load it along with the other 
[`somaverse`](http://bitbucket.sladmin.com/projects/SV) packages
using the `RStudio` **addin** feature, which behaves similar to 
`devtools::load_all()`.

```
Addins Menu ->
  SOMAOBJECTS ->
    `Load Development Environment`
```

Alternatively, you may call the driver function directly from `SomaObjects`:

```{r}
# Help
?SomaObjects::sp

# Direct Call
# Note: all objects, even non-exported, are accessible
SomaObjects::sp()
ls("package:devel")
```


----------

#### LICENSE

Please note that this SomaLogic, Inc. internal package is released with 
a [LICENSE](LICENSE). By using in this package you agree to abide by its terms.


-------------------------


Created on `r Sys.Date()` by [Rmarkdown](https://github.com/rstudio/rmarkdown)
(v`r utils::packageVersion("rmarkdown")`) and `r R.version$version.string`. 
